\documentclass[10pt, letterpaper]{article}


% Packages:
\input{packages}
% Settings:
\input{settings}

\begin{document}
    \newsavebox\ANDbox
    \sbox\ANDbox{$|$}

    \begin{header}
        \fontsize{25 pt}{25 pt}\selectfont Mycola Kolomiiets

        \vspace{5 pt}

        \normalsize
        \mbox{Kyiv, Ukraine}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{mailto:nickkolomietsdooor@gmail.com}{nickkolomietsdooor@gmail.com}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{tel:+380 672 570 278}{+380 672 570 278}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://itytell.github.io/site/}{Portfolio site}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://www.linkedin.com/in/mycola-kolomiiets-5350961b0/}{linkedin}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://github.com/ItyTell}{github}}%
    \end{header}

    \vspace{5 pt - 0.3 cm}

    \section{Education}
        
        \begin{twocolentry}{
            September 2020 – June 2024
        }
            \textbf{Taras Shevchenko national university of Kyiv}, 
            faculty - Computer Science and Cybernetics, department - Computational Mathematics
        \end{twocolentry}

        \vspace{0.10 cm}
        \begin{onecolentry}
            \begin{highlights}
                \item GPA: 89/100
            \end{highlights}
        \end{onecolentry}



    
    \section{Experience}

     
        \begin{twocolentry}{
            August – October 2023
        }
            \textbf{Fellow of the program "IRIS-HEP Fellow 2023"}, Prinston university, CERN \end{twocolentry}

        \vspace{0.10 cm}
        \begin{onecolentry}
            During the program, I collaborated with specialists in the fields of software development and data science on project related to high particle physics
        \end{onecolentry}

    \section{Language}
        

        \begin{samepage}
            \textbf{English, B2}


            I think I have B2 level, due to a small number of errors on the external examination and on the EVI. 
            I have experience working with foreign colleagues and teachers Most of the content I consumed for 4 years was in English, so language comprehension is at a high level however, there was not much speaking practice.


            \textbf{Ukrainian, native}

        \end{samepage}

    \section{Skills}

            
        \begin{onecolentry}
            \begin{highlightsforbulletentries}


            \item Python

            At university, I took a year-long course in Python. 
            I used it to automate calculations in other subjects and create personal projects, such as a telegram bot to provide some statistics and a simple 2-D game on pygame. 
            The last algorithms I implemented in Python were some clustering algorithms: k-means, fuzzy k-means (a variation of the previous one) and DBScan. 
            I also used python for my thesis on predicting levels of harmful emissions in the atmosphere.


            \item Math
            

            I graduated with a degree in applied mathematics. 
            I studied various branches of mathematics, including statistics, probability theory, numerical methods and mathematical analysis.


            \item Deep learning
            

            I took a course on Coursera “Deep Learning Specialization” from Deep Learning.AI and received a certificate in 2023.
            Then I played around with the acquired knowledge in Jupyter Notebook, creating and training several neural networks.
            I applied neural networks in my graduate thesis and in personal projects, and also worked with neural networks in the fellow program.

            \item Git, Docker, Linux
            

            I use git for all of my projects and have experience with git and dicker after my fellow program.
            I used to have a Linux computer, now I use Linux mainly with WSL to use GPU in tensorflow (my main computer has Windows).
            
            
            \item C++
            

            I took a year-long C++ course at university. 
            The course was mostly about the object-oriented paradigm, but all the examples and assignments were in C++.


            \item SQL
            

            At university, I took a half-year SQL course. 
            During the course, I learned how to write queries of varying complexity, including very complex ones. 
            The course was based on Microsoft Access, although later I applied the knowledge I gained while working on a Python-based telegram bot, for which I initially wanted to use SQLite, but settled on MySQL.
            

            \end{highlightsforbulletentries}
        \end{onecolentry}

\end{document}